Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-20 WSSSPE1_report/WSSSPE1_summary_report.tex
minor changes

Additional volunteers:
\begin{itemize}
\item Chris Mattmann $\langle$\url{chris.a.mattmann@jpl.nasa.gov}$\rangle$
\item * Ketan Maheshwari $\langle$\url{ketancmaheshwari@gmail.com}$\rangle$
\item Marlon Pierce $\langle$\url{marpierc@iu.edu}$\rangle$
\item Colin Venters $\langle$\url{C.Venters@hud.ac.uk}$\rangle$
\item Suresh Marru $\langle$\url{smarru@iu.edu}$\rangle$
\item Lynn Zentner $\langle$\url{lzentner@purdue.edu}$\rangle$
\item Anne Elster $\langle$\url{anne.elster@gmail.com}$\rangle$
\item Shel Swenson $\langle$\url{mdswenso@usc.edu}$\rangle$
\item Andy Ray Terrel $\langle$\url{andy.terrel@gmail.com}$\rangle$
\item Abani Patra $\langle$\url{abani.patra@gmail.com}$\rangle$
\item * Nancy Wilkins-Diehr $\langle$\url{wilkinsn@sdsc.edu}$\rangle$
\item James Spencer $\langle$\url{j.spencer@imperial.ac.uk}$\rangle$
\item * Frank L\"{o}ffler $\langle$\url{knarf@cct.lsu.edu}$\rangle$
\item * James Hetherington $\langle$\url{j.hetherington@ucl.ac.uk}$\rangle$
\item * Sou-Cheng (Terrya) Choi $\langle$\url{sou.cheng.terrya.choi@gmail.com}$\rangle$
\item James Howison $\langle$\url{james@howison.name}$\rangle$
\item * Bruce Berriman $\langle$\url{gbb@ipac.caltech.edu}$\rangle$
\item Hilmar Lapp $\langle$\url{hlapp@nescent.org}$\rangle$
\item * Marcus D. Hanwell $\langle$\url{marcus.hanwell@kitware.com}$\rangle$
\item Lucas Nussbaum $\langle$\url{lucas.nussbaum@loria.fr}$\rangle$
\item Matthew Turk $\langle$\url{matthewturk@gmail.com}$\rangle$
\end{itemize}

@@

\subsection{Utility Software}
Utility software potentially has the broadest community impact of the three
categories. This is
especially relevant in the modern era of social computing. In the context of
this paper, a utility software project could be defined as general purpose software
applicable to one or many generic tasks and/or enabling other software to run
by providing a suitable environment. Examples are collaborative development
framework such as \emph{GitHub} and \emph{Bitbucket}, Workflow and scripting
frameworks such as \emph{Galaxy}, \emph{Swift} and \emph{VisTrails},
and visualization frameworks such as \emph{visIT}. Often projects start with
specific, small set of requirements and users in mind but expand to provide
more generic functionality and appeal to a wider user community.

@@

The following is a partial list of attendees who were recorded on the
Google doc~\cite{WSSSPE1-google-notes} that was being used for live note taking at the workshop, with some additions made by the authors of this paper.

\begin{multicols}{4}
\setlength{\parindent}{0pt}
%in theory, should save the old value then set it back after this section, but since this is the end...

>>>>

Additional volunteers:
\begin{itemize}
\item Chris Mattmann $\langle$\url{chris.a.mattmann@jpl.nasa.gov}$\rangle$
\item * Ketan Maheshwari $\langle$\url{ketancmaheshwari@gmail.com}$\rangle$
\item Marlon Pierce $\langle$\url{marpierc@iu.edu}$\rangle$
\item Colin Venters $\langle$\url{C.Venters@hud.ac.uk}$\rangle$
\item Suresh Marru $\langle$\url{smarru@iu.edu}$\rangle$
\item Lynn Zentner $\langle$\url{lzentner@purdue.edu}$\rangle$
\item Anne Elster $\langle$\url{anne.elster@gmail.com}$\rangle$
\item * Shel Swenson $\langle$\url{mdswenso@usc.edu}$\rangle$
\item Andy Ray Terrel $\langle$\url{andy.terrel@gmail.com}$\rangle$
\item Abani Patra $\langle$\url{abani.patra@gmail.com}$\rangle$
\item * Nancy Wilkins-Diehr $\langle$\url{wilkinsn@sdsc.edu}$\rangle$
\item James Spencer $\langle$\url{j.spencer@imperial.ac.uk}$\rangle$
\item * Frank L\"{o}ffler $\langle$\url{knarf@cct.lsu.edu}$\rangle$
\item * James Hetherington $\langle$\url{j.hetherington@ucl.ac.uk}$\rangle$
\item * Sou-Cheng (Terrya) Choi $\langle$\url{sou.cheng.terrya.choi@gmail.com}$\rangle$
\item James Howison $\langle$\url{james@howison.name}$\rangle$
\item * Bruce Berriman $\langle$\url{gbb@ipac.caltech.edu}$\rangle$
\item Hilmar Lapp $\langle$\url{hlapp@nescent.org}$\rangle$
\item * Marcus D. Hanwell $\langle$\url{marcus.hanwell@kitware.com}$\rangle$
\item Lucas Nussbaum $\langle$\url{lucas.nussbaum@loria.fr}$\rangle$
\item Matthew Turk $\langle$\url{matthewturk@gmail.com}$\rangle$
\end{itemize}

@@

\subsection{Utility Software}
Utility software potentially has the broadest community impact of the three
categories. This is
especially relevant in the modern era of social computing. In the context of
this paper, a utility software project could be defined as general purpose software
applicable to one or many generic tasks and/or enabling other software to run
by providing a suitable environment. Examples are collaborative development
framework such as \emph{GitHub} and \emph{Bitbucket}, workflow and scripting
frameworks such as \emph{Galaxy}, \emph{Swift}, and \emph{VisTrails},
and visualization frameworks such as \emph{visIT}. Often projects start with
specific, small set of requirements and users in mind but expand to provide
more generic functionality and appeal to a wider user community.

@@

The following is a partial list of attendees who were recorded on the
Google doc~\cite{WSSSPE1-google-notes} that was being used for live note taking at the workshop, or by the SC13 student volunteers, with some additions also made by the authors of this report.

\begin{multicols}{3}
\setlength{\parindent}{0pt}
%in theory, should save the old value then set it back after this section, but since this is the end...
